# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

_The data is already in the repos (activity.zip)_

1. Unzip the file
2. Read the csv
3. Transform the date column

```{r echo=TRUE, cache=TRUE}

unzip("activity.zip", c("activity.csv"))
activity <- read.csv("activity.csv")
activity$date <- as.Date(activity$date)

# let's see what's inside:
summary(activity)

```


## What is mean total number of steps taken per day?

Here's some exploration of the data. A Histogram of a total number of steps of each day. At the end, the mean and median of total number of steps per day

```{r echo=TRUE, cache=TRUE}
library(ggplot2)

# calculate the number steps by day
steps_a_day <- aggregate(activity$steps,
                         by=list(activity$date),
                         FUN=sum)

# change the names
names(steps_a_day) <- c("date", "steps")

# histogram of steps/day
chart <- ggplot(steps_a_day) +
    aes(date, steps) +
    geom_histogram(stat="identity")

print(chart)


# getting  mean and median values
steps_mean <- mean(steps_a_day$steps, na.rm=T)
steps_median <- median(steps_a_day$steps, na.rm=T)

# Mean total number of steps per day
print(steps_mean)

# Median total number of steps per day
print(steps_median)



```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
